dyngen: simulating developing single cells

### 2019-09-19 content.tex
update

@@

\comment{GRN is defined nowhere}

@@

\comment{could use figure; one with GRNs of different topologies, another with rewiring events}

@@

\comment{explain what is meant by 'sampling' and 'profiling technique' a little better}

@@

\comment{show that dyngen output resembles real data using e.g. countsimQC?}

\comment{add result figures pertaining use cases}

@@

\comment{also adding more types of molecules, e.g. protein complex, small rnas, PPI}
\section{Methods}
\comment{The method section is REALLY rough at this stage.}

@@

\comment{mention strength and cooperativity.}

@@

\subsection{Generate gene regulatory network}
\comment{Welcome to the beginning of the end}

@@

\comment{TODO: add step-by-step  derivation of transcription formula}
% regG,H represents a 'probability' that H is bound to G (though does not yet scale between [0,1]). y_H / maxy_H is more likely to be a probability that H is bound to G, though this does not take into account that H can be bound to other genes as well. 
% in any case, if it is, then it upregulates G by strG,H. It is assumed binding events
% are independent and result in multiplicative effect.

@@

\comment{→ basically an ODE}
When simulating the developmental backbone, we go through the edges of the backbone state network defined in an earlier step (Section \ref{sec:backbone}), starting from the root state. It is assumed the root state has no modules active and has no expression of any molecules. To get to next state, we follow a transition starting from the root state, activate and deactivate the modules as indicated by the transition, and compute the average molecule abundance along the transition. To compute the average abundance, we perform small time steps $t = 0.001$ and let each reaction (Section \ref{sec:reactions}) occur $t$ times its propensity.

>>>>

% DYNGEN CONTENT

@@

\mycomment{GRN is defined nowhere}

@@

\mycomment{could use figure; one with GRNs of different topologies, another with rewiring events}

@@

\mycomment{explain what is meant by 'sampling' and 'profiling technique' a little better}

@@

\mycomment{show that dyngen output resembles real data using e.g. countsimQC?}

\mycomment{add result figures pertaining use cases}

@@

\mycomment{also adding more types of molecules, e.g. protein complex, small rnas, PPI}
\section{Methods}
\mycomment{The method section is REALLY rough at this stage.}

@@

\mycomment{mention strength and cooperativity.}

@@

\subsection{Generate gene regulatory network}
\mycomment{Welcome to the beginning of the end}

@@

\mycomment{TODO: add step-by-step  derivation of transcription formula}
% regG,H represents a 'probability' that H is bound to G (though does not yet scale between [0,1]). y_H / maxy_H is more likely to be a probability that H is bound to G, though this does not take into account that H can be bound to other genes as well. 
% in any case, if it is, then it upregulates G by strG,H. It is assumed binding events
% are independent and result in multiplicative effect.

@@

\mycomment{→ basically an ODE}
When simulating the developmental backbone, we go through the edges of the backbone state network defined in an earlier step (Section \ref{sec:backbone}), starting from the root state. It is assumed the root state has no modules active and has no expression of any molecules. To get to next state, we follow a transition starting from the root state, activate and deactivate the modules as indicated by the transition, and compute the average molecule abundance along the transition. To compute the average abundance, we perform small time steps $t = 0.001$ and let each reaction (Section \ref{sec:reactions}) occur $t$ times its propensity.
